Hijacking Malaria Simulators with Probabilistic Programming

### 2019-04-27 paper/icml_ai4good/main.tex

Ensemble methods are commonly used in statistics in order to combine the predictive power of multiple models \cite{}. To this end, recent work has attempted to characterise the similarities and differences between two of the most advanced Malaria epidemiology simulators, EMOD \cite{} and OpenMalaria \cite{}. Evaluation is usually done by comparing a number of output parameters across a range of hand-crafted standard scenarios reflecting different geographical locations across Africa. \cite{Smith}.

@@

We provide examples of the generated trace plots from the connection between the simulator and the PPS in Figure~\ref{fig:plotewan}. 
When comparing the two trace plots between EMOD and OpenMalaria we see significant differences, despite both evaluating the same model for the same disease.

We can see from the addressing schemes $A_1, \ldots, A_N$ \ref{table:addresses}\ref{table:asingleaddress} what physical events are connected to each other and how outputs in EMOD are generated from a different set of procedures as compared to OpenMalaria 
By having access to such diagrams users can internally evaluate and scrutinize the decisions that the simulator is making.

@@

for those with severe Malaria infections \\
\bottomrule
  \end{tabularx}
  \end{table}
\bibliographystyle{icml2019}
\bibliography{malaria,refs}

\end{document}

>>>>

Ensemble methods are commonly used in statistics in order to combine the predictive power of multiple models \cite{cameron2015defining,smith_ensemble_2012}. To this end, recent work has attempted to characterise the similarities and differences between two of the most advanced Malaria epidemiology simulators, EMOD \cite{bershteyn2018implementation} and OpenMalaria \cite{smith2008towards}. Evaluation is usually done by comparing a number of output parameters across a range of hand-crafted standard scenarios reflecting different geographical locations across Africa~\cite{smith_ensemble_2012}.

@@

We provide examples of the generated trace plots from the connection between the simulator and the PPS in Figure~\ref{fig:plotewan}. 
We can see from the addressing schemes $A_1, \ldots, A_N$ \ref{table:addresses}\ref{table:asingleaddress} what physical events are connected to each other and how outputs in EMOD are generated from a different set of procedures as compared to OpenMalaria 
By having access to such diagrams users can internally evaluate and scrutinize the decisions that the simulator is making.

@@

for those with severe Malaria infections \\
\bottomrule
  \end{tabularx}
  \end{table}

\section{Discussions and Future Work}

\paragraph{Discussion} In this work we have demonstrated a method 
that enables one to hijack population based simulators, extending 
the work of \citep{baydin2018efficient}. 
We applied our method to two Malaria orientated population-based simulators and 
generated a variety of trace graphs.
Finally, we have shown how our system
enables policy makers and non-experts to analyse simulator outputs in a 
way previously unavailable in the field of epidemiology.

\paragraph{Future Work} To extend our work further we aim to implement additional 
tools that will facilitate complicated inference procedures that condition on simulator 
output.

\bibliographystyle{icml2019}
\bibliography{malaria,refs}
\end{document}
